{\small Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}

### 2017-11-13 Meetings/GPMNov2017/gpm_november2017_topic21.tex
improvement on gpm

\begin{frame}{L-Mode analysis: I$_p$ scan at constant q$_{95}$}
\Fontvi
  \vspace{-1cm}
  \begin{columns}    
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantQ95}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
    \centering{\includegraphics<3>[height=\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantQ95}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}}
    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/n0_CurrentScanConstantQ95}}
    \centering{\includegraphics<7>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantq95_samedensity}}
    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}}
    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantQ95}}
    \centering{\includegraphics<10>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantQ95}}

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> AUG: All the shots were performed in the so-called
        Edge Optmized Configuration (EOC) shape
      \item<1|only@1> AUG: We matched correctly the shape and the L$_{\parallel}$
        here shown from outer divertor plate up to X-point 
      \item<2|only@2> AUG: The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early
        disruption
      \item<2|only@2> AUG: The total power (Ohmic plus NBI) was kept
        constant throughout the scan
      \item<2|only@2> AUG: We have comparable edge density, divertor neutral
        pressure and divertor temperature
      \item<3|only@3> TCV: We repeat the same excercise at TCV with a
        slight difference in the profile of parallel connection
        length. This required operation at unusual low toroidal field
        (up to 0.8T)
      \item<4|only@4> TCV: no additional heating
        used. Nevertheless the difference in power crossing the separatrix
        is small
      \item<4|only@4> TCV: The difference in target pressure similar
        to AUG behavior
      \item<5|only@5> AUG: At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current. \alert{We have flattening of the upstream
          profiles only when $\Lambda_{div}$ is well above one on all
          the profile}
      \item<6|only@6> Neutrals estimated using calibrated D$_{\alpha}$
        images coupled with values of density and temperature at the
        target suggest a larger   
      \item<7|only@7> TCV: This tendency is not observed for TCV where
        profiles seem resilient to modification of Bt even though we
        reached pretty high value of $\Lambda_{div}$ all along the profile.
      \item<8|only@8> TCV: This is due to the fact that we can't
        observed during the density ramp any signature of rollover or detachment,
        whereas upstream profile modification at TCV are only observed
        well after rollover
      \item<9|only@9> AUG: There is the tendency towards larger blobs
        at lower current
      \item<10|only@10> TCV: this is not confirmed for TCV but in line
        with the lack of shoulder and detachment
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

\begin{frame}{L-Mode analysis: I$_p$ scan at constant B$_{t}$}
\Fontvi
  \vspace{-1cm}
  \begin{columns}    
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantBt}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}}
    \centering{\includegraphics<3>[height=\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantBt}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}}
    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantBt_Profiles_UsDiv}}
    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/n0_CurrentScanConstantBt}}
    \centering{\includegraphics<7>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantBt_samedensity}}
    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantBt}}
    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantBT}}
    \centering{\includegraphics<10>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantBt}}

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> AUG: We matched correctly the shape the parallel
        connection length L$_{\parallel}$ is modified consistently
      \item<1|only@1> AUG: The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early disruption
      \item<2|only@2> AUG: We have comparable edge density and divertor neutral
        pressure even though pressure increase earlier at higher current
      \item<2|only@2> AUG: The total power (Ohmic plus NBI) was kept
        constant throughout the scan
      \item<3|only@3> TCV: We repeat the same excercise at TCV with a
        consistent variation of parallel connection length
      \item<4|only@4> TCV: no additional heating
        used. Nevertheless the difference in power crossing the separatrix
        is small
      \item<4|only@4> TCV: Neutral compression is roughly constant between
      \item<5|only@5> AUG: At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current. \alert{We have flattening of the upstream
          profiles only when $\Lambda_{div}$ is well above one on all
          the profile}
        \item<6|only@6> Neutrals at lower current are substantially
          higher even with similar edge density profiles.
      \item<7|only@7> TCV: This tendency is substantially confirmed at
        TCV where
        profiles  
      \item<8|only@8> TCV: This is consistent with onset of detachment
        (at least in intermediate and lower current)
      \item<9|only@9> AUG: While the general observation of increasing
        blob size with $\Lambda_{div}$ is confirmed there are no
        differences between the current
      \item<10|only@10> TCV: confirm the observation of AUG. 
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

@@

\begin{frame}{H-Mode effect of puffing location}

\begin{frame}{H-Mode effect of cryopumps}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Shot_34276_34278_InterELMprofiles}
      \includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/Shot_34278_34281_InterELMprofiles}
    \end{column}
    \begin{column}{0.5\textwidth}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{Comments on different divertor geometry which can be explored}

>>>>

\begin{frame}{L-Mode analysis: I$_p$ scan at constant q$_{95}$}
\Fontvi
  \vspace{-1cm}
  \begin{columns}    
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantQ95}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
    \centering{\includegraphics<3>[height=\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantQ95}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}}
    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/n0_CurrentScanConstantQ95}}
    \centering{\includegraphics<7>[width=.6\textheight]{../../Experiments/AUG/analysis/pdfbox/RadiationPeakDensityIpScan_constantQ95}}
    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantq95_samedensity}}
    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}}
    \centering{\includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantQ95}}
    \centering{\includegraphics<11>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantQ95}}

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> AUG: All the shots were performed in the so-called
        Edge Optmized Configuration (EOC) shape
      \item<1|only@1> AUG: We matched correctly the shape and the L$_{\parallel}$
        here shown from outer divertor plate up to X-point 
      \item<2|only@2> AUG: The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early
        disruption
      \item<2|only@2> AUG: The total power (Ohmic plus NBI) was kept
        constant throughout the scan
      \item<2|only@2> AUG: We have comparable edge density, divertor neutral
        pressure and divertor temperature
      \item<3|only@3> TCV: We repeat the same excercise at TCV with a
        slight difference in the profile of parallel connection
        length. This required operation at unusual low toroidal field
        (up to 0.8T)
      \item<4|only@4> TCV: no additional heating
        used. Nevertheless the difference in power crossing the separatrix
        is small
      \item<4|only@4> TCV: The difference in target pressure similar
        to AUG behavior
      \item<5|only@5> AUG: At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current. \alert{We have flattening of the upstream
          profiles only when $\Lambda_{div}$ is well above one on all
          the profile}
      \item<6|only@6> AUG: Neutrals estimated using calibrated D$_{\alpha}$
        images coupled with values of density and temperature at the
        target suggest a larger   
      \item<7|only@7> AUG: At all the current a clear roll-over in
        peak density observed and we can also track the radiation
        front move away from target earlier in density at lower current
      \item<8|only@8> TCV: This tendency is not observed for TCV where
        profiles seem resilient to modification of Bt even though we
        reached pretty high value of $\Lambda_{div}$ all along the profile.
      \item<9|only@9> TCV: This is due to the fact that we can't
        observed during the density ramp any signature of rollover or detachment,
        whereas upstream profile modification at TCV are only observed
        well after rollover
      \item<10|only@10> AUG: There is the tendency towards larger blobs
        at lower current
      \item<11|only@11> TCV: this is not confirmed for TCV but in line
        with the lack of shoulder and detachment
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

\begin{frame}{L-Mode analysis: I$_p$ scan at constant B$_{t}$}
\Fontvi
  \vspace{-1cm}
  \begin{columns}    
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantBt}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}}
    \centering{\includegraphics<3>[height=\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantBt}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}}
    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantBt_Profiles_UsDiv}}
    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/n0_CurrentScanConstantBt}}
    \centering{\includegraphics<7>[width=.65\textheight]{../../Experiments/AUG/analysis/pdfbox/RadiationPeakDensityIpScan_constantBT}}
    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantBt_samedensity}}
    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantBt}}
    \centering{\includegraphics<10>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantBT}}
    \centering{\includegraphics<11>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantBt}}

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> AUG: We matched correctly the shape the parallel
        connection length L$_{\parallel}$ is modified consistently
      \item<1|only@1> AUG: The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early disruption
      \item<2|only@2> AUG: We have comparable edge density and divertor neutral
        pressure even though pressure increase earlier at higher current
      \item<2|only@2> AUG: The total power (Ohmic plus NBI) was kept
        constant throughout the scan
      \item<3|only@3> TCV: We repeat the same excercise at TCV with a
        consistent variation of parallel connection length
      \item<4|only@4> TCV: no additional heating
        used. Nevertheless the difference in power crossing the separatrix
        is small
      \item<4|only@4> TCV: Neutral compression is roughly constant between
      \item<5|only@5> AUG: At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current. \alert{We have flattening of the upstream
          profiles only when $\Lambda_{div}$ is well above one on all
          the profile}
        \item<6|only@6> Neutrals at lower current are substantially
          higher even with similar edge density profiles.
        \item<7|only@7> Neutrals at lower current are substantially
          higher even with similar edge density profiles.
      \item<8|only@8> TCV: This tendency is substantially confirmed at
        TCV where
        profiles  
      \item<9|only@9> TCV: This is consistent with onset of detachment
        (at least in intermediate and lower current)
      \item<10|only@10> AUG: While the general observation of increasing
        blob size with $\Lambda_{div}$ is confirmed there are no
        differences between the current
      \item<11|only@11> TCV: confirm the observation of AUG. 
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

@@

\begin{frame}{H-Mode investigation: puffing location}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=0.85\textheight]{../../Experiments/AUG/analysis/pdfbox/PuffingLocation}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34277}}
    \only<3>{
      \begin{tikzonimage}[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34277}
        \draw [->, ultra thick, white] (0.2, 0.45) -- (0.3, 0.55);
        \draw [->, ultra thick, white] (0.62, 0.45) -- (0.72, 0.55);
      \end{tikzonimage}   
    }
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1-> Similar puff from Lower and Upper divertor valves
        (\alert{we asked for divertor/midplane valves})
      \item<2-> Discharge with a total amount 6.5 heating power
        with equivalent behavior also in the lower divertor
        independently from the puffing location
      \item<3-> Edge density profiles from Li-Beam evolution are
        pretty similar
      \item<3|alert@3> Similar behavior observed from RIC Antenna 4
        for the available shot
    \end{itemize}
  \end{column}
\end{columns}
\end{frame}

\begin{frame}{Compare fueling with/without cryopumps}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34278}}
    \centering{\includegraphics<2>[height=.65\textheight]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34278}}
    \only<3>{
    \begin{tikzonimage}[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34278}
      \draw [->, ultra thick, white] (0.2, 0.45) -- (0.3, 0.55);
      \draw [->, ultra thick, dashed, red] (0.62, 0.45) -- (0.72, 0.55);
    \end{tikzonimage}}
  \centering{\includegraphics<4>[height=.85\textheight]{../../Experiments/AUG/analysis/pdfbox/Shot_34276_34278_InterELMprofiles}}
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
    \item<1-> Same fueling but with cryo-pumps
      \item<1-> H-5 density is different and remain constant, both
        divertor and midplane pressure are reduced (to 1/3
        approximately) no sign of detachment
      \item<2-> Different ELMy regimes reached with reduced size and
        increased frequency without the cryopumps
      \item<3-> Also with this amount of fueling weaker indication of SOL
        saturation observed as confirmed by Li-Beam and by RIC (Antenna 4)
      \item<4> Inter-ELM resolved profile suggest a flattening even
        with the cryompumps still even though $\Lambda_{div}$ is
        marginal above 1 only in the near SOL

    \end{itemize}
  \end{column}
\end{columns}
\end{frame}

\begin{frame}{Matching scenarios with cryo-pumps}
\Fontvi
  \vspace{-1cm}
\begin{columns}
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/CompareShot34276_34281}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/PuffingIpolsola34276_34281}}
    \centering{\includegraphics<3>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/EvolutionEdgeProfiles_34276_34281}}
    4\centering{\includegraphics<4>[height=0.9\textheight]{../../Experiments/AUG/analysis/pdfbox/Shot_34278_34281_InterELMprofiles}}
  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1-> To match similar edge density and divertor pressure
        and to reach the same level of detachment we increase the
        fueling by almost a factor of 3, increasing also the rate. In
        addition to that we also increase substantially the N
        puffing. \alert{Degraded H-Mode reached earlier in density
          without the cryopumps}
      \item<2-> Similar ELMy behavior obtained during the density ramp  
      \item<3-> Without cryopumps evidence of stronger SOL profile
        flattening from Li-Be. \alert{To be compared with appropriate
          variation of $\Lambda_{div}$}
       \item<4> Inter-ELM resolved Li-Be profiles 
    \end{itemize}
  \end{column}
\end{columns}
\end{frame}

\begin{frame}{Comments on difficulties for H-Mode in TCV}

\end{frame}
\begin{frame}{Comments on different divertor geometry which can be explored}
